\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-04 paper/main.tex
add preliminary figure "correlation of regressors" at the top of main.tex

23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top XY phonemes \tabularnewline

@@

>>>>

23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top 80 phonemes \tabularnewline

@@

% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied. In this way, long-time-scale components in the model will be dealt with correctly. This is set with the Apply temporal filtering option.”
\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/regressor-corr}
  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation. Regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation. Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
  \label{fig:correlation}
\end{figure*}
